\hyphenation{diffe-rent}
%%%%%%%%%%%%%%%%%%%%% acknowlegments %%%%%%%%%%%%%%%%%

This is the time to thank all the people that made possible the starting of the dream and the ending of an stage. I would like to thank my advisers Kenneth Bloom, Aaron Dominguez for their professional and personal support, they are definitely a model to follow. A big thank you to Benjamin Stieger; this thesis would not have been possible without your support and patience. I am very fortunate to have joined the UNL HEP group where I found wonderful people willing to talk, discuss, teach and learn.

My stay at CERN was full of experiences; from the enriching exposures presenting my contributions in the \ttH and \HWW analysis meetings - where again Benjamin was always having my back, thanks again man! - to the guided visits to the CMS experiment and CERN visitor itineraries. Thank you to all the members of these analysis groups for your valuable feedback. Thank you also to all the amazing groups of visitors that made my pasion for CMS to show up again when the hard times came to me; a small tribute for you is at the end of this document.

My total recognition goes to all the members of the CMS experiment for making possible the operation of such a marvelous machine and the entire collaboration, as well as to the U.S.A National Science Foundation (NSF) for supporting our adventures. 

I had a great time in the Silicon Lab making not only FPix modules but friends. Bob Kelty, Brian, Joaquin, Caleb, Frank, Rachel, Pat, Bob Rhynalds, Savanna, Levi, Kevin, Ashton, thanks for all the long journeys of work full of histories, jokes, complains and fixes, support, etc; we did it! and at a high level.

I would like to thank professor Peter Dowben for being such a great person and model for Ele and me.

Many thanks to Dr. Elena Echeverria and Dr$_{{\footnotesize soon}}$. Rami Kamalieddin for their invaluable role as editors and reviewers of this thesis. Also to the members of my committee from whom I only got impressive guidance. 

But not all has been work, and the responsibles for the great times out of the lab are the ``Latinos'' - who are not only latinos -, partners of parties, picnics, soccer, dance and discussions. A big thank you to Isa, Mao, Xime, Alvaro, Joaquin, Josefa, Carolina, Jairo -alias Carlos-, Meli, Juan, Rafa, Hollman, Aleja, A.J., Luis, Carla, Jilmar, Jorge, Martha, Julieta, Omar, David, who were and are supporting my Ele while I am far from home. 

Looking back to the past I notice that challenging times come accompanied by great people. Every day I feel the warm from the Y-107, extended to Y-106 and beyond; Luis, Javier, Maru, Camilo, Augusto, Paula, Juliana, Edwin, you guys are the best family somebody could get.    

The dream started with a couple of guys pushing me to get in to the university and now, 20 years later, here I am giving you a victory report! Jaime and Juan this is yours too. At that time, people felt lucky for having expensive clothes; I was and I am fortunate for having you guys.

The end of this stage is also accompanied by another great guy; Rami, bro you are the best!.

Soy muy afortunado de pertenecer a una familia de guerreros; Pa y Ma, nada de esto habria sido posible sin su esfuerzo y sacrificio, todo lo que soy y lo que sere viene de ustedes. Juancho, Caro, Pao, Laura, Gustavo, Diana, Chago, Cacenza, Clema, Eduardo, Luigi, Lili, Tia, Marisol, Nico, Hija, Lise and Jamir, gracias por tanto apoyo y amor. A mis sobrinos, Juli, Dany, Yeyo, Sarai, Ana Maria, Thomas, Mariana, Kevin and Many por ser mi motivo para continuar, ya vendran los tiempos de caminar juntos. A mis parceros del Mazuera, no se imaginan cuanto me han hecho la vida con tanto material.

Ele, you know you are my all, nothing make sense without you, so, vamos pa'lante! ``ya que hpts''.  

I want to dedicate these last lines to thank my advisers Ken, Aaron and Ben for their strong commitment in promoting my career further, I will do my best to make your effort worthwhile.   






